### 2011-01-26 trunk/htdocs/user.tex
Added comments on LE constraints to user.tex
git-svn-id: https://ccpforge.cse.rl.ac.uk/svn/ludwig@1240 40876441-3496-0410-a613-a2fca35b2ae2

>>>>

Note that if something more complicated is required, for example,
an equilibration at zero shear followed by a run with shear, one
needs to be careful how this is arranged. The code works out the
current displacement of the planes by computing $U_{LE} t$, where
$t$ is the current time step. A shear run should then start from
$t = 0$, otherwise an offset is required. At the moment this cannot
be done via the input.

\subsubsection{Lees-Edwards planes in parallel}

There are a couple of additional constraints to use the Lees-Edwards
planes in parallel. In particular, the planes cannot fall at a
processor boundary in the $x$-direction. This means you should
arrange an integer number of planes per process in the $x$-direction.
(For example, use one plane per process; this will also ensure the number
of planes
still evenly divides the total system size.)
This will interleave the planes with the processor decomposition.
The $y$-direction and $z$-direction may be decomposed without
further constraint.

Note that this means a simulation with one plane will only work
if there is one process in the $x$ decomposition.
